### 2015-03-23 Paper1Editted/paper1Beditted.tex
New figure + new manuscript

While we treat both the process and actuator as dynamic models in our derivation, it is important to note that both the derivation and the technique are agnostic to the process model. Even if the process model was a reverberating loop \cite{fortney2012computational} driven by a reference intent, we might still recover that reference intent by inverting the loop. We are not limited to dynamic models as this might be extended to a lookup table. For instance, a switch is well-modeled as a lookup table or threshold without any consideration of its underlying mechanism. In this case, our technique could be used to determine a person's intention to flip the switch and how it changes in the face of disturbance. As long as some bidirectional relationship  exists between state and outcome (even if determined empirically), intended outcome can be determined. This allows determination of intent in many situations of interest, even where the process is irreducibly complex.

@@

\subsection*{Statistical Analysis}
Our principal goal was to determine if and when disturbed trajectories departed from undisturbed trajectories. To detect this departure, we use the one-tailed Student's t-test $(\alpha=.05)$ at 5 millisecond intervals to determine whether or not the deviation of the disturbed trajectories had exceeded the maximum deviations of the undisturbed trajectories. The spans between departure of the hand and estimated intent were compared against 120 milliseconds using the Wilcoxon signed rank test. The MATLAB statistics toolbox package \cite{MATLAB:2008} was used for all comparisons.

@@

These results suggested a reproducible approach for inspecting how individuals might alter their intent in response to disturbances. Actual hand paths could no longer be explained ($p=0.05$) by deviation in undisturbed movement within 145 milliseconds after the onset of disturbance. While some subjects' intents showed no significant from baseline despite disturbance, when intent deviated it did so 150-255 milliseconds after the hand deviated (Figure 3B). When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred later, the intent continued to the target, but interestingly, it then corrected (Figure 3A). Intention showed systematic deflections that counteracted the direction of disturbance beginning about 200 milliseconds after the onset of the force disturbance; however, this counteraction did not immediately depart from the range of undisturbed movements (Figure 4, orange region). Hand movements returned to undisturbed levels of error within 600 milliseconds, but intention did not always return to undisturbed levels within one second.

@@

The proposed approach could explain the discovery by Bizzi et al. \cite{bizzi1984posture} of a ``virtual trajectory'' ($\alpha$) in deafferented monkeys that progressed smoothly from the initial to final positions and how that virtual trajectory is different from $\lambda$, the equilibrium point of muscles -- $x_d$ and $\lambda$ are equivalent only when $x_d$ is unchanging.  By deriving the technique in a general form, we discovered that our $x_d$ is equivalent to $\alpha$ and can be used to determine the muscle equilibrium of a $\lambda$ model.

Interestingly, the formulation leads to some implications on the expected behavior of this moving equilibration. Even if the muscle equilibrium jumped abruptly, this would be insufficient to move the intended trajectory abruptly due to the presence of the mass term in the intention formulation -- reaching intent cannot jump abruptly. The intent trajectories certainly follow this pattern, smoothly responding to disturbances at a latency of about 200 milliseconds. While this work examines the tendencies of the onset of change, statistical testing cannot be used to detect the absence of change in an individual movement. Still, Figure 3 shows reaches that are more compatible with intermittent control than with continuous optimal feedback control. In classic optimal control, the system is always updating intent in response to error \cite{todorov2002optimal}. While most of our subjects displayed a latent response consistent with sensory feedback latencies \cite{pruszynski2012optimal}, three subjects showed no detectable response. The absence of a response to a large force disturbance within an optimal feedback control framework and is instead consistent with adherence to a trajectory planned before any disturbance. Alternatively,  control that is intermittent \cite{gawthrop2011intermittent} with limited opportunities to change intent can explain both change and lack thereof. It remains to be seen if and how change in intent might be triggered.

@@

While we use the terms \textit{intent}, $x_d$, and \textit{equilibrium trajectory of the arm} interchangeably, they are not always identical. We assume that action does not deviate from intent in the absence of external disturbance. For this to be true, $x_d$ must be the intent. Not all action need arise from a continuous intent trajectory, however. One might volitionally twitch a muscle without planning its effect on the limb. In the context of reaching, our results and others' \cite{flash1991arm, bizzi1984posture, shadmehr1994adaptive, rohrer2004submovements, fortney2012computational, mistry2013optimal} suggest a continuous pre-planned trajectory with kinematic constraints, perhaps composed in an intermittent fashion from some motor primitive. Outside of this context, the word \textit{intent} may often be inappropriate.

>>>>

While we treat both the process and actuator as dynamic models in our derivation, it is important to note that both the derivation and the technique are agnostic to the process model. Even if the process model was a reverberating loop \cite{fortney2012computational} driven by a reference intent, we might still recover that reference intent by simulating the loop. We are not limited to dynamic models as this might be extended to a lookup table. For instance, a switch is well-modeled as a lookup table or threshold without any consideration of its underlying mechanism. In this case, our technique could be used to determine a person's intention to flip the switch and how it changes in the face of disturbance. As long as some bidirectional relationship  exists between state and outcome (even if determined empirically), intended outcome can be determined. This allows determination of intent in many situations of interest, even where the process is irreducibly complex.

@@

\subsection*{Statistical Analysis}
Our principal goal was to determine if and when disturbed trajectories departed from undisturbed trajectories. To detect this departure, we use the one-tailed Student's t-test $(\alpha=.05)$ at 5 millisecond intervals to determine whether or not the deviation of the disturbed trajectories had exceeded the maximum deviations of the undisturbed trajectories. The span between departure of the hand and estimated intent was compared against 120 milliseconds using the sign test. The MATLAB statistics toolbox package \cite{MATLAB:2008} was used for all comparisons.

@@

These results suggested a reproducible approach for inspecting how individuals might alter their intent in response to disturbances. Actual hand paths could no longer be explained ($p=0.05$) by deviation in undisturbed movement within 145 milliseconds after the onset of disturbance. Despite the disturbance, three subjects' intents did not depart significantly from baseline. The remaining five subjects' intents deviated between 150 and 255 milliseconds after the hand deviated (Figure 3B). When disturbances occurred early in reaching, intent showed some signs of correction mid-reach. When disturbances occurred later, the intent continued to the target, but interestingly, it then corrected (Figure 3A). Intention showed systematic deflections that counteracted the direction of disturbance beginning about 200 milliseconds after the onset of the force disturbance; however, this counteraction did not immediately depart from the range of undisturbed movements (Figure 3B, orange region). This counteraction is consistent with both change of intent and stiffening in response to the disturbance.

@@

The proposed approach could explain the discovery by Bizzi et al. \cite{bizzi1984posture} of a ``virtual trajectory'' ($\alpha$) in deafferented monkeys that progressed smoothly from the initial to final positions and how that virtual trajectory is different from $\lambda$, the equilibrium point of muscles -- $x_d$ and $\lambda$ are equivalent only when $x_d$ is unchanging; therefore, this muscle equilibrium cannot be the intent of a movement. By deriving the technique in a general form, we discovered that our $x_d$ is equivalent to $\alpha$ and can be used to determine the muscle equilibrium of a $\lambda$ model.

Interestingly, the formulation leads to some implications on the expected behavior of this moving equilibration. Even if the muscle equilibrium jumped abruptly, this would be insufficient to move the intended trajectory abruptly due to the presence of the mass term in the intention formulation -- reaching intent cannot jump abruptly. The intent trajectories certainly follow this pattern, smoothly responding to disturbances at a latency of about 200 milliseconds. While this work examines the tendencies of the onset of change, statistical testing cannot be used to detect the absence of change in an individual movement. Still, Figure 3 shows reaches that are more compatible with intermittent control than with continuous optimal feedback control. In classic optimal control, the system is always updating intent in response to error \cite{todorov2002optimal}. While most of our subjects displayed a latent response consistent with sensory feedback latencies \cite{pruszynski2012optimal}, three subjects showed no detectable response. The absence of response to a large force disturbance seems inconsistent with optimal feedback control framework and is instead consistent with adherence to a trajectory planned before the disturbance. Control that is intermittent \cite{gawthrop2011intermittent} with limited opportunities to change intent can explain both change and lack thereof. It remains to be seen if and how change in intent might be triggered.

@@

While we use the terms \textit{intent}, $x_d$, and \textit{equilibrium trajectory of the arm} interchangeably, they are not always identical. We assume that action does not deviate from intent in the absence of external disturbance. For this to be true, the equilibrium trajectory of the arm must be the intent. Not all action need arise from a continuous intent trajectory, however. One might volitionally twitch a muscle without planning its effect on the limb. In the context of reaching, our results and others' \cite{flash1991arm, bizzi1984posture, shadmehr1994adaptive, rohrer2004submovements, fortney2012computational, mistry2013optimal} suggest a continuous pre-planned trajectory with kinematic constraints, perhaps composed in an intermittent fashion from some motor primitive. This planned trajectory may not itself be intended and might arise from an intent to minimize cost or effort.
